---
title: "R Notebook"
author: "Jacob Hallowell"
output: html_notebook
---

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
```

The goal of this test is to create the Runs Created Stat for the Ground Sloths, as well as an attempt to visualize other stats.
```{r}
sloths_stat <- read.csv('sloths CSVs/sloths_stats_6-2.csv', skip = 1, header = TRUE)
```
This loads in any file we choose on the computer. It also formats the file as long as it is a CSV from gamechanger.

With all of these columns of data it makes it hard to mutate and add columns like RC. I could attempt to remove pitching stats but still. I think the best thing to do is to create new separate tables and map from there.

For example, I am going to create a new table selecting only the stats I want.
```{r}
hit_stats <-
  sloths_stat %>%
  select("Number","First","Last","GP","PA","AB","X1B","X2B","X3B","H","HR","RBI","R","BB","SO","AVG","OBP","SLG","OPS","SB","XBH","TB")

hit_stats <- transform(hit_stats, GP = as.numeric(GP),
                       PA = as.numeric(PA),
                       AB = as.numeric(AB),
                       X1B = as.numeric(X1B),
                       X2B = as.numeric(X2B),
                       X3B = as.numeric(X3B),
                       H = as.numeric(H),
                       HR = as.numeric(HR),
                       BB = as.numeric(BB),
                       SO = as.numeric(SO),
                       AVG = as.numeric(AVG),
                       OBP = as.numeric(OBP),
                       SLG = as.numeric(SLG),
                       OPS = as.numeric(OPS),
                       SB = as.numeric(SB),
                       XBH = as.numeric(XBH),
                       TB = as.numeric(TB))
hit_stats <- hit_stats[-c(26, 27), ]
```